fdcoexist

### 2018-10-16 meta_simulations.Rmd
Implemented other simuls with high/low k with same A

```{r normal_k}
# Simulation parameters --------------------------------------------------------
normal_k = 1.15
normal_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        normal_k)

# Actual simulation -----------------------------------------------------------
plan(multiprocess)
tictoc::tic()
normal_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

@@

```{r low_k_same_A}
# Simulation parameters --------------------------------------------------------
low_k = 1.05
low_k_same_A_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        normal_k)

# Actual simulation -----------------------------------------------------------
plan(multiprocess)
tictoc::tic()
low_k_same_A_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

@@

```{r normal_k_same_A}
# Simulation parameters --------------------------------------------------------
normal_k = 1.05
high_A = 2e-2
normal_k_same_A_run_char = paste0("N = ", total_runs, "; A = ", high_A,
                                  "; B = ", B, "; k = ",
                                  normal_k)

# Actual simulation -----------------------------------------------------------
plan(multiprocess)
tictoc::tic()
normal_k_high_A_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, given_k = normal_k, given_A = high_A)
}, .progress = FALSE)
tictoc::toc()
```

@@

```{r normal_k_paper_figures}
# Simpler Figures ----------------------------------------------------------------------
# Show shape of CWM <-> across situations
plot_normal_k_cwm_env = normal_k_simuls %>%
    bind_rows() %>%
    filter(!(scenario %in% c("R75A25", "R25A75")),
           compet_status %in% "compet") %>%
    ggplot(aes(patch_optim, trait2_cwm, color = fct_rev(cor_level),
               group = interaction(cor_level, seed_number))) +
    geom_line(aes(group = interaction(cor_level, seed_number)), alpha = 1/20) +
    geom_smooth(aes(group = cor_level), se = FALSE) +
    facet_grid(rows = vars(env_width), cols = vars(scenario),
               labeller = lab_compet_env) +
    scale_color_viridis_d("Correlation", labels = lab_cor) +
    labs(x = "Environment",
         y = "Trait 2 CWM",
         title = paste0("CWM <-> Env. Relationship across N = ", total_runs,
                           " sets of traits"),
         subtitle = paste0("opaque line = smoothed average\n",
                           "background lines = individual simulations")) +
    theme(panel.grid = element_blank(),
          legend.position = "top")
plot_normal_k_cwm_env

plot_normal_k_slope_constant_env = normal_k_simuls_slope %>%
    filter(env_width != "varying", compet_status == "compet",
           !(scenario %in% c("R75A25", "R25A75"))) %>%
    ggplot(aes(scenario, estimate)) +
    geom_violin(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9), draw_quantiles = 0.5) +
    facet_grid(rows = vars(env_width), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, 1) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("Slope of Trait 2 CWM ~ environment ",
                           "with Constant Env. Filter\n",
                           normal_k_run_char),
         x = "Scenario",
         y = "Slope") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

>>>>

```{r normal_k}
# Competition == Environmental Filtering
# Simulation parameters --------------------------------------------------------
normal_k = 1.15
normal_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ",
                           B, "; k = ", normal_k)

# Actual simulation -----------------------------------------------------------
plan(multiprocess, workers = availableCores() - 2)
tictoc::tic()
normal_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

@@

```{r low_k_same_A}
# Competition >> Environmental filtering
# Simulation parameters --------------------------------------------------------
low_k = 1.05
low_k_same_A_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ",
                               B, "; k = ", low_k)

# Actual simulation -----------------------------------------------------------
tictoc::tic()
low_k_same_A_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

@@

```{r high_k_same_A}
# Competition << Environmental Filtering
# Simulation parameters --------------------------------------------------------
high_k = 1.4
high_k_same_A_run_char = paste0("N = ", total_runs, "; A = ", A,
                                  "; B = ", B, "; k = ",
                                  high_k)

# Actual simulation -----------------------------------------------------------
tictoc::tic()
high_k_same_A_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, given_k = high_k, given_A = A)
}, .progress = FALSE)
tictoc::toc()
```

@@

```{r paper_figures}
# Show shape of CWM <-> across situations --------------------------------------
all_simuls = list(normal_k_normal_A = normal_k_simuls,
                  high_k_normal_A   = high_k_same_A_simuls,
                  low_k_normal_A    = low_k_same_A_simuls) %>%
    purrr::map_df(bind_rows, .id = "simul_param")

plot_all_k_cwm_env = all_simuls %>%
    filter(!(scenario %in% c("R75A25", "R25A75")),
           compet_status == "compet",
           env_width == "constant") %>%
    ggplot(aes(patch_optim, trait2_cwm, color = fct_rev(cor_level),
               group = interaction(cor_level, seed_number))) +
    geom_line(aes(group = interaction(cor_level, seed_number)), alpha = 1/20) +
    geom_smooth(aes(group = cor_level), se = FALSE) +
    facet_grid(rows = vars(simul), cols = vars(scenario),
               labeller = lab_compet_env) +
    scale_color_viridis_d("Correlation", labels = lab_cor) +
    labs(x = "Environment",
         y = "Trait 2 CWM",
         title = paste0("CWM <-> Env. Relationship across N = ", total_runs,
                           " sets of traits"),
         subtitle = paste0("opaque line = smoothed average\n",
                           "background lines = individual simulations")) +
    theme(panel.grid = element_blank(),
          legend.position = "top")
plot_normal_k_cwm_env

# Slope in function of scenario & competition status ---------------------------
plot_normal_k_slope_constant_env = normal_k_simuls_slope %>%
    filter(env_width != "varying", compet_status == "compet",
           !(scenario %in% c("R75A25", "R25A75"))) %>%
    ggplot(aes(scenario, estimate)) +
    geom_violin(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9), draw_quantiles = 0.5) +
    facet_grid(rows = vars(env_width), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, 1) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("Slope of Trait 2 CWM ~ environment ",
                           "with Constant Env. Filter\n",
                           normal_k_run_char),
         x = "Scenario",
         y = "Slope") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
